timesliced_random_cell_selection

### 2018-11-19 src/biological_data_prep.Rmd
background depth layer name

>>>>

rename the lat/long meters columns and remove the duplicate column

```{r}
names(data_aea)[names(data_aea)=="decimalLongitude.1"] <- "longitude_meters"
names(data_aea)[names(data_aea)=="decimalLatitude.1"] <- "latitude_meters"
data_aea <- subset(data_aea, select = -c(decimalLongitude.1.1, decimalLatitude.1.1))
head(data_aea)
```

### 2018-11-19 src/timesliced_random_cell_selection.Rmd
background depth layer name

```{r}
head(background_all)
```
ok so some more crap has been added - the year and month both have _ appended.... change this. Also change glo_unique_cell to cell_id

```{r}
names(background_all)[names(background_all)=="year_"] <- "year"
names(background_all)[names(background_all)=="month_"] <- "month"
names(background_all)[names(background_all)=="glo_unique_cell"] <- "cell_id"
head(background_all)
```

@@

>>>>

```{r}
head(background_all)
```
ok so some more crap has been added - the year and month both have _ appended.... change this. Also change 
- glo_unique_cell to cell_id
- longitude to longitude_meters
- latitude to latitude_meters

and remove
- optional
- x.1
- x
- id_depth

```{r}
names(background_all)[names(background_all)=="year_"] <- "year"
names(background_all)[names(background_all)=="month_"] <- "month"
names(background_all)[names(background_all)=="glo_unique_cell"] <- "cell_id"
names(background_all)[names(background_all)=="longitude"] <- "longitude_meters"
names(background_all)[names(background_all)=="latitude"] <- "latitude_meters"
background_all <- subset(background_all, select = -c(optional, X.1, X, id_depth))
head(background_all)
```

@@

still need
-bottom_depth
-depth_layer
-total_cell_obs
-yymm_cell_obs

#depth layer
